\chapter{Those Damn Bugs!}

One thing to be aware of is that \prog\ is under development, so there
are some features built into it which may or may not be permanent.
We've tried to indicate wherever possible when things are not finished
or are in the testing stages.


\section{What is a bug?}

There are two possible reasons for a calculation to screw up: a bug in
the program or a user error.  Please make sure that your input file is
correct before you send in a bug report.

Any of the following things could indicate a
bug:

\begin{enumerate}

\item \calcprog\ gives you answers that don't make any sense at all

\item \calcprog\ does something funny like not printing out something
you told it to print out.

\item \calcprog\ wanders off into space and never comes back (i.e. it
runs forever).

\item \calcprog\ crashes without giving you some idea of what
happened.

\item \calcprog\ seg faults and dies. (You see the message: {\tt
Segmentation Fault: core dumped})

\end{enumerate}

We have yet to see \calcprog\ do anything like \#3 above.  If you do
think that the run is taking too long, check the status file and make
sure that it is still doing something.

\calcprog\ should {\bf never} do either \#4 or \#5 above.  If either
of these happen you have definitely found a bug.  {\bf Please report it}.
The major cause of segmentation faults seems to be problems in the
input files given to \calcprog. Error checking routines are in place to
catch many of these problems, but we probably missed a
few.  So please let us know if you find input file formats that give
rise to segmentation faults without generating a warning.

\viewprog\ is a slightly different story.  The code for \viewprog\
isn't nearly as clean or carefully written as that in \calcprog.  The
result is that \viewprog\ occasionally will dump core and/or die
unexpectedly. We're aware of some of these problems and are working on
them.  If you can make \viewprog\ dump core reproducibly, please let
us know.  Similarly, if the output from \viewprog\ just looks wrong,
tell us and we'll see what we can do.

\section{What to do if you find a bug}

In order for us to be able to fix bugs, we have to be able to reproduce
the circumstances that gave rise to them.  In order to do this, we need
a copy of the input file that caused the problem.  Please include the
following in any bug report that you send:

\begin{enumerate}

\item A description of what went wrong, or why you think the answers
you got are wrong.

\item Copies of the input file (essential), and the status and output
files (optional, but extremely useful).

\item Information about what kind of computer you are using (machine
type and operating system version if possible).

\item Some way to get in touch with you.

\end{enumerate}

Please send bug reports to the following email address:

{\tt yaehmop@xtended.chem.cornell.edu}

